\documentclass{article}
\usepackage{amsmath,amssymb,graphicx}
\usepackage{color}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{natbib}

\usepackage{xr-hyper}
\usepackage{hyperref}

\usepackage[margin=2.5cm]{geometry}

\setlength{\parindent}{0em}
\setlength{\parskip}{1em}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Response to Typesetter \#1}
 
We thank the typesetter for their feedback on our manuscript. In our responses below, quoted page and line numbers correspond to the proof copy: \texttt{egusphere-2025-4351-typeset\_manuscript-version1.pdf}.

In addition to our comments below, we would like to request updating all manuscript figures with updated versions that address minor changes in formatting. We have made adjustments to figure size and whitespace to ensure plot elements are centered (e.g., legends and colorbars) and that all figure text follows a consistent font size. In the typeset PDF, Figures 2, 12, 13, and 14 span the width of a single text column.  We have adjusted the size of these single-column figures so that the figure elements and text are scaled appropriately. Furthermore, we have made minor stylistic changes to all figures, such as removing borders around figure legends, increased grid resolution in figures spanning a single text column, and an increased number of x-tick markers in some figures to improve legibility. In replacing all figures, we would like to request that the typesetter use the same figure width formatting as provided in the typesetting PDF and simply replace all figures with the updated version we provide here.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{(TS1)} Please check updated capitalization in the title/running title.

\begin{quote}
    The updated capitalization is correct. 
\end{quote}

\textbf{(TS2)} Please check throughout the text that all vectors are denoted by bold italics and matrices by bold roman.

\begin{quote}
    The use of bold symbols in Equation 1 is incorrect; the variable $D$ should not be bold. Equation 1 and text on page 4, lines 58--63 should appear as the following:\\
    ``For a discrete 2-dimensional scalar field $f$ over a domain $S$ with lateral
    dimensions $N$ by $M$, $\eta$ is defined as

    \begin{equation}
    \eta(f, S) = \frac{2\sum_{\tilde{S}\in D}|\overline{f}(S) - \overline{f}(\tilde{S})|}{MN\overline{f}(S)\left[3MN-M-N-1\right]}, 
    \end{equation}
    where $\overline{f}(S)$ is the domain mean, $\overline{f}(\tilde{S})$ is the mean over a subset of the domain
    $\tilde{S}$, and $D$ is the set of all possible subdomains.'' 

\end{quote}

\textbf{(TS3)} Please check and confirm adjustments made to the equation to fit the two-column-layout.

\begin{quote}
    We would prefer Equation 2 (page 13, lines 14--18) to be displayed without a line break. We suggest the following simplified expression which reduces notational complexity while retaining clarity, 

    ``The percent difference is calculated as 
        \begin{equation}
            \% \text{ difference} = 100\times\left(\frac{\overline{[\mathrm{CCN}]}_{\text{Scenario}} - \overline{[\mathrm{CCN}]}_{\text{No het.}}}{\overline{[\mathrm{\mathrm{CCN}}]}_{\text{No het.}}}\right),
        \end{equation}
    where $\overline{[\mathrm{CCN}]}$ is the horizontally averaged
    concentration of CCN at time $t$ and vertical level $z$ that activate
    at supersaturation $S_{\mathrm{env}}$.''
\end{quote}

\textbf{(TS4)} Please provide date of last access.

\begin{quote}
    All links in the Code and data availability section (page 18 lines 104--105 and page 19 lines 1--13) were last accessed on 3 April 2026.
\end{quote}

\textbf{(TS5)} Please confirm that your interactive computing environment (10.13012/B2IDB-9622921\_V3) provides a well-defined structure for data, code, text, documentation, runtime environment, and user interface controls for a piece of research. An interactive computing environment should be complete in a way that everything one needs to execute is available and no other assets must be downloaded. If this is the case, please provide an Interactive computing environment (ICE) statement with DOI and citation. If this is not the case, we will insert it as code availability.

\begin{quote}
    The interactive computing environment definition does not apply to our code repository. 10.13012/B2IDB-9622921\_V3 contains processed simulation output and code for generating figures, but does not include the model code necessary to run simulations described in this manuscript. Model code is contained in the Zenodo archive mentioned in the code availability statement. 
\end{quote}

\textbf{(TS6)} Please note that the funding information has been added to this paper. Please check if it is correct. Please also double-check your acknowledgements to see whether repeated information can be removed or changed accordingly. Thanks.

\begin{quote}
    We would like to suggest the following formatting for the Financial support section (page 19, lines 40--42): \\
    ``This research has been supported by the U.S. Department of Energy, Office of Science, Biological and Environmental Research program (grant no. DE-SC0022130), and by the National Science Foundation, Directorate for Geosciences (grant no. AGS 19-41110).'' \\ 

    Alongside these changes, we request the acknowledgements be removed. 
\end{quote}

\textbf{(TS7)} Please check; should this be updated with the final revised version at \url{https://www.mdpi.com/2073-4433/14/7/1136?}

\begin{quote}
    Thank you for identifying this error. Below is the correct citation (page 19, lines 46--49):\\
    ``Brasseur, G. P., Barth, M., Kazil, J., Patton, E. G., and
    Wang, Y.: Segregation of Fast-Reactive Species in
    Atmospheric Turbulent Flow, Atmosphere, 14, 1136,
    https://doi.org/10.3390/atmos14071136, 2023.''
\end{quote}

\textbf{(TS8)} Please provide DOI or page range.

\begin{quote}
    The DOI for the requested paper (page 20, lines 96--98) is \url{https://doi.org/10.1021/es00077a009}.
\end{quote}

\end{document}